Randomise papers for DOM Review

### 2025-03-04 Supplement/Code/Randomisation.qmd
Major changes to MS over the past two weeks prior to resubmission

---
title: Randomise papers for DOM Review
subtitle: Describes random selection of papers for inclusion in the review
author: Saoirse Kelleher
date: today
format: 
  html:
    code-fold: true
    theme: minty
    toc: true
    embed-resources: true
---

@@

```{r load WOS queries}
keyTerms_datasheet <- read_xlsx("Queries/Final Queries/Keywords.xlsx",
                                skip = 10) |>
  select(Title, Year = "Publication Year", Journal = "Source Title", 
         Authors, Citations = "Total Citations", DOI) |>
  mutate(Query = "KeyTerms")

citesMackenzie_datasheet <- read_xlsx("Queries/Final Queries/MacKenzie_A.xlsx",
                                      skip = 10) |>
  rbind(read_xlsx("Queries/Final Queries/MacKenzie_B.xlsx",
                  skip = 10)) |>
  select(Title, Year = "Publication Year", Journal = "Source Title", 
         Authors, Citations = "Total Citations", DOI) |>
  mutate(Query = "CitesMackenzie")
```

@@

```{r Save sheet}
write_csv(randomised_datasheet, "Randomisation/Final_Randomisation.csv")
```

>>>>

---
title: Randomise papers for DOM Review
subtitle: Describes random selection of papers for inclusion in the review
date: July 29 2024
format: 
  html:
    theme: minty
    toc: true
    embed-resources: true
---

@@

```{r load WOS queries}
keyTerms_datasheet <- read_xlsx("Queries/Keywords.xlsx",
                                skip = 10) |>
  select(Title, Year = "Publication Year", Journal = "Source Title", 
         Authors, Citations = "Total Citations", DOI) |>
  mutate(Query = "KeyTerms")

citesMackenzie_datasheet <- read_xlsx("Queries/MacKenzie_A.xlsx",
                                      skip = 10) |>
  rbind(read_xlsx("Queries/MacKenzie_B.xlsx",
                  skip = 10)) |>
  select(Title, Year = "Publication Year", Journal = "Source Title", 
         Authors, Citations = "Total Citations", DOI) |>
  mutate(Query = "CitesMackenzie")
```

@@

```{r Save sheet}
write_csv(randomised_datasheet, "Randomisation.csv")
```
